Development of Autograder For Competitive Programming Using Contestant PC As Worker

### 2019-06-30 src/paper.tex
fix pagination

Based on the development and testing we have done, there are some lessons we learned.
\begin{enumerate}
    \item There is a high grading performance improvement in UGrade compared to many online judges that are currently popular. This performance improvement is caused by the number of the worker in the UGrade which follows the number of contestants in the competition.
    \item The grading performance of UGrade is not affected by the number of contestants but affected by the grading size number of UGrade. The high number of contestant causes a high number of worker too, so that doesn't affect the grading performance. However, the grading size number causes the number of submission doubles, thus affects the grading performance.
    \item The high number of grading size reduce grading performance but increase system security. The low number of grading size increase grading performance but reduce system security. The juries need to adjust the grading size to achieve the best result.
    \item The security of UGrade needs further research. However, we can use UGrade to organize some types of online judge competition where the contestant don't have root access to their computer such as ACM-ICPC competition.
    \item UGrade can keep the fairness of grading process even if the worker computers have different specification and performance. UGrade achieves this by comparing the jury's solution and contestant's solution in the same computer.
    \item Pull-based load balancing of UGrade causes the UGServer load to become very huge. The load balancing method of this system needs further research.
\end{enumerate}

>>>>

Based on the development and testing we have done, there are some lessons we learned.
\begin{enumerate}
    \item There is a high grading performance improvement in UGrade compared to many online judges that are currently popular. This performance improvement is caused by the number of the worker in the UGrade which follows the number of contestants in the competition.
    \item The grading performance of UGrade is not affected by the number of contestants but affected by the grading size number of UGrade. The high number of contestant causes a high number of worker too, so that doesn't affect the grading performance. However, the grading size number causes the number of submission doubles, thus affects the grading performance.
    \item The high number of grading size reduce grading performance but increase system security. The low number of grading size increase grading performance but reduce system security. The juries need to adjust the grading size to achieve the best result.
    \item The security of UGrade needs further research. However, we can use UGrade to organize some types of online judge competition where the contestant don't have root access to their computer such as in ACM-ICPC.
    \item UGrade can keep the fairness of grading process even if the worker computers have different specification and performance. UGrade achieves this by comparing the jury's solution and contestant's solution in the same computer.
    \item Pull-based load balancing of UGrade causes the UGServer load to become very huge. The load balancing method of this system needs further research.
\end{enumerate}
